A Way Forward in Parallelising Dynamic Languages

### 2014-05-05 talk/icooolps2014/position-paper.tex
another comment

In the end, fine-grained locking can transparently replace the GIL
and therefore parallelise existing applications, generally without any
changes\footnote{There are rare cases where not having atomic
bytecodes actually changes the semantics.}
It does however not provide a better synchronisation
mechanism to the application like e.g. atomic blocks.

\cfbolz{I think you should mention the commented out point below, that a lot of existing code contains latent races / deadlocks that are just not exposed in a GIL-full world}
%% - support of atomic blocks?\\
%% - hard to get right (deadlocks, performance, lock-granularity)\\
%% - very hard to get right for a large language\\
%% - hard to retro-fit, as all existing code assumes GIL semantics\\
%% - (there are some semantic differences, right? not given perfect lock-placement, but well)
%% ( http://www.jython.org/jythonbook/en/1.0/Concurrency.html )

>>>>

In the end, fine-grained locking can transparently replace the GIL and
therefore parallelise existing applications, generally without any
changes\footnote{There are rare cases where not having atomic
  bytecodes actually changes the semantics.}. An implementation has to
follow the GIL semantics very closely, otherwise it may expose some
latent data races in existing applications which are just not exposed
with a GIL. This approach does however not provide a better parallelising
synchronisation mechanism to the application like e.g. atomic blocks.

%% - support of atomic blocks?\\
%% - hard to get right (deadlocks, performance, lock-granularity)\\
%% - very hard to get right for a large language\\
%% - hard to retro-fit, as all existing code assumes GIL semantics\\
%% - (there are some semantic differences, right? not given perfect lock-placement, but well)
%% ( http://www.jython.org/jythonbook/en/1.0/Concurrency.html )
